---
title: "hw04"
author: "Shashwat Singh"
format: html
editor: visual
description: "Regression in R"
---

## **Dataset Description**

This dataset consists of the daily stock prices and volume of 14 different tech companies, including Apple (AAPL), Amazon (AMZN), Alphabet (GOOGL), and Meta Platforms (META) and more!

## **Question to be Answered**

How do daily opening prices, trading volumes, and historical trends influence the adjusted closing prices of stocks?

## **Install Required Packages**

```{r}
# Required packages
if (!require(pacman))
  install.packages("pacman")

pacman::p_load(tidymodels,
               tidyverse,
               ranger,
               randomForest,
               glmnet,
               gridExtra)

# Global ggplot theme
theme_set(theme_bw() + theme(legend.position = "top"))
```

## Import Dataset

```{r}

# Reading the CSV from the URL
stocks<- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_stock_prices.csv')

#Initial analysis of dataset
stocks|> head()
```

## Regression

Regression is a modeling technique for predicting quantitative-valued target attributes. The goals for this tutorial are as follows: 1. To provide examples of using different regression methods from the tidymodels package.

2. To demonstrate the problem of model overfitting due to correlated attributes in the data.

3. To illustrate how regularization can be used to avoid model overfitting.

## **Stock Data Generation**

To illustrate how linear regression works, we first generate a random 1-dimensional vector of predictor variables, x, from a uniform distribution. The response variable y has a linear relationship with x according to the following equation: y = -3x + 1 + epsilon, where epsilon corresponds to random noise sampled from a Gaussian distribution with mean 0 and standard deviation of 1.

```{r}
# Parameters
seed <- 1 # Setting seed to 1           
numInstances <- nrow(stocks) #Assigning number of rows 

# Set seed
set.seed(seed)

# Assigning y=f(x) such that we are checking whether closing price is a function of open price
X <- stocks$open
y_true <- stocks$close

# Adding Gaussian Additive noise
y <- y_true + matrix(rnorm(numInstances), ncol=1)

# Plot
ggplot() +
  geom_point(aes(x=X, y=y), color="black") +
  geom_line(aes(x=X, y=y_true), color="blue", linewidth=1,alpha=0.5) +
  ggtitle('Relation Between Closing and Opening Price') +
  theme_minimal()+
  xlab('Open') +
  ylab('Close')
```

-   The data looks linear in nature and the opening price show a direct relation with the closing price.

## **Multiple Linear Regression** 

We will use Python's scikit-learn package to fit a multiple linear regression (MLR) model.

Given a training set X,y MLR is designed to learn f(X,w)=X^T^w +w~0~ by minimizing the following loss function given a training set

L(y,f(X,w)) = (i=1 to n)∑ \|\|y~i-~ X~i~w-w~0~\|\|

where w (slope) and w0 (intercept) are the regression coefficients.

Given the input dataset, the following steps are performed:

1\. Split the input data into their respective training and test sets.

2\. Fit multiple linear regression to the training data.

3\. Apply the model to the test data.

4\. Evaluate the performance of the model.

5\. Postprocessing: Visualizing the fitted model.

#### Step 1: Split Input Data into Training and Test Sets

```{r}
# Train/test split
numTrain <- 20   # number of training instances
numTest <- numInstances - numTrain

set.seed(123) # For reproducibility

data <- tibble(X = X, y = y)

split_obj <- initial_split(data, prop = numTrain/numInstances)

# Extract train and test data
train_data <- training(split_obj)
test_data <- testing(split_obj)

# Extract X_train, X_test, y_train, y_test
X_train <- train_data$X
y_train <- train_data$y

X_test <- test_data$X
y_test <- test_data$y


# Train/test split
library(rsample)

numTrain <- 5000
numTest <-numInstances - numTrain

set.seed(123)

data <- tibble(X=X, y=y)

split_obj <-initial_split(data, prop = numTrain/numInstances)

# Extract train and test data 

train_data <- training(split_obj)
test_data <-  testing(split_obj)

# Extract X_train, X_test , y_train, y_test

X_train <-train_data$X
y_train <-train_data$y

X_test <- test_data$X
y_test <- test_data$y
```
