---
title: "hw04"
author: "Shashwat Singh"
format: html
editor: visual
description: "Regression in R"
---

## **Dataset Description**

This dataset consists of the daily stock prices and volume of 14 different tech companies, including Apple (AAPL), Amazon (AMZN), Alphabet (GOOGL), and Meta Platforms (META) and more!

## **Question to be Answered**

How do daily opening prices, trading volumes, and historical trends influence the adjusted closing prices of stocks?

## **Install Required Packages**

```{r}
# Required packages
if (!require(pacman))
  install.packages("pacman")

pacman::p_load(tidymodels,
               tidyverse,
               ranger,
               randomForest,
               glmnet,
               gridExtra)

# Global ggplot theme
theme_set(theme_bw() + theme(legend.position = "top"))
```

## Import Dataset

```{r}

# Reading the CSV from the URL
stocks<- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-07/big_tech_stock_prices.csv')

#Initial analysis of dataset
stocks|> head()
```

## Regression

Regression is a modeling technique for predicting quantitative-valued target attributes. The goals for this tutorial are as follows:  1. To provide examples of using different regression methods for the stock prices dataset.

2.  To demonstrate the problem of model overfitting due to correlated attributes in the data.

3.  To illustrate how regularization can be used to avoid model overfitting.

## **Stock Data Generation**

```{r}
# Parameters
seed <- 1 # Setting seed to 1           
numInstances <- nrow(stocks) #Assigning number of rows 

# Set seed
set.seed(seed)

# Assigning y=f(x) such that we are checking whether closing price is a function of open price
X <- stocks$open
y_true <- stocks$adj_close

# Adding Gaussian Additive noise
y <- y_true + matrix(rnorm(numInstances), ncol=1)

# Plot
ggplot() +
  geom_point(aes(x=X, y=y), color="black") +
  geom_line(aes(x=X, y=y_true), color="blue", linewidth=1,alpha=0.5) +
  ggtitle('Relation Between Adjusted Closing and Opening Price') +
  theme_minimal()+
  xlab('Open') +
  ylab('Adj. Close')
```

-   The data looks linear in nature and the opening price show a direct relation with the adjusted closing price. For the datapoints between values 100-200, the plot becomes a little non-linear, but overall, a linear relation can be seen.

## **Multiple Linear Regression**

We will use Python's scikit-learn package to fit a multiple linear regression (MLR) model.

Given a training set X,y MLR is designed to learn f(X,w)=X^T^w +w~0~ by minimizing the following loss function given a training set

L(y,f(X,w)) = (i=1 to n)∑ \|\|y~i-~ X~i~w-w~0~\|\|

where w (slope) and w0 (intercept) are the regression coefficients.

Given the input dataset, the following steps are performed:

1\. Split the input data into their respective training and test sets.

2\. Fit multiple linear regression to the training data.

3\. Apply the model to the test data.

4\. Evaluate the performance of the model.

5\. Postprocessing: Visualizing the fitted model.

#### Step 1: Split Input Data into Training and Test Sets

```{r}
# Train/test split
numTrain <- 1000   # number of training instances
numTest <- numInstances - numTrain

set.seed(123) # For reproducibility

data <- tibble(X = X, y = y)

split_obj <- initial_split(data, prop = numTrain/numInstances)

# Extract train and test data
train_data <- training(split_obj)
test_data <- testing(split_obj)

# Extract X_train, X_test, y_train, y_test
X_train <- train_data$X
y_train <- train_data$y

X_test <- test_data$X
y_test <- test_data$y


```

-   Splitting the data into Training and Test sets for Validation(to avoid overfitting)

#### Step 2: Fit regression model to Training Set

```{r}
# Create a linear regression model specification
lin_ref_spec <-  linear_reg() |>
  set_engine("lm")


# Fit the model to the training data
lin_reg_fit <-lin_ref_spec |>
  fit(y~ X, data = train_data)


```

-   Fitting the created model to the training set

#### Step 3: Apply Model to the Test Set

```{r}

# Apply model to the test set 
y_pred_test <- predict(lin_reg_fit, new_data =test_data) |>
  pull(.pred)

```

-   Applying the model to the test dataset(The model trained on training data has never seen test data)

#### Step 4: Evaluate Model Performance on the test set

```{r}
# Plotting true vs predicted values
ggplot() + 
  geom_point(aes(x = as.vector(y_test), y = y_pred_test), color = 'blue') +
  ggtitle('Comparing true and predicted values for test set') +
  xlab('True values for y') +
  ylab('Predicted values for y')

```

-   We can see from the plot that the the predicted and true values are close to each other. The model has performed well on the test data.

```{r}
# Prepare data for yardstick evaluation
eval_data <- tibble(
  truth = as.vector(y_test),
  estimate = y_pred_test
)

# Model evaluation
rmse_value <- rmse(data = eval_data, truth = truth, estimate = estimate)
r2_value <- rsq(eval_data, truth = truth, estimate = estimate)

cat("Root mean squared error =", sprintf("%.4f", rmse_value$.estimate), "\n")
```

-   The relatively low RMS value(considering that we are trying to predict stock prices which are highly volatile) suggests that the true and predicted values are very close to each other.

```{r}
cat('R-squared =', sprintf("%.4f", r2_value$.estimate), "\n")
```

Rsquared value of 0.9889 suggests that the model performs well on new data and generalises well.

#### Step 5: Postprocessing

```{r}
# Display model parameters
coef_values <- coef(lin_reg_fit$fit)  # Extract coefficients
slope <- coef_values["X"]
intercept <- coef_values["(Intercept)"]

cat("Slope =", slope, "\n")


```

-   Slope is positive i.e. the Close Price is directly proportional to Open Price.

```{r}
cat("Intercept =", intercept, "\n")
```

```{r}
### Step 4: Postprocessing

# Plot outputs
ggplot() +
  geom_point(aes(x = as.vector(X_test), y = as.vector(y_test)), color = 'black') +
  geom_line(aes(x = as.vector(X_test), y = y_pred_test), color = 'blue', linewidth = 1) +
  ggtitle(sprintf('Predicted Function: y = %.2fX + %.2f', slope, intercept)) +
  xlab('X') +
  ylab('y')
```

-   The output function shows that the relationship is almost perfectly linear, i.e very close to y=x

## **Effect of Correlated Attributes**

We will illustrate how the presence of correlated attributes can affect the performance of regression models.

```{r}

# Considering other features in the dataset
set.seed(1)
X2 <- stocks$high
X3 <- stocks$low
X4 <- stocks$close
X5 <- stocks$volume

# Create plots
plot1 <- ggplot() +
  geom_point(aes(X, X2), color='black') +
  xlab('X') + ylab('X2') +
  ggtitle(sprintf("Correlation between X and X2 = %.4f", cor(X[-c((numInstances-numTest+1):numInstances)], X2[-c((numInstances-numTest+1):numInstances)])))

plot2 <- ggplot() +
  geom_point(aes(X2, X3), color='black') +
  xlab('X2') + ylab('X3') +
  ggtitle(sprintf("Correlation between X2 and X3 = %.4f", cor(X2[-c((numInstances-numTest+1):numInstances)], X3[-c((numInstances-numTest+1):numInstances)])))

plot3 <- ggplot() +
  geom_point(aes(X3, X4), color='black') +
  xlab('X3') + ylab('X4') +
  ggtitle(sprintf("Correlation between X3 and X4 = %.4f", cor(X3[-c((numInstances-numTest+1):numInstances)], X4[-c((numInstances-numTest+1):numInstances)])))

plot4 <- ggplot() +
  geom_point(aes(X4, X5), color='black') +
  xlab('X4') + ylab('X5') +
  ggtitle(sprintf("Correlation between X4 and X5 = %.4f", cor(X4[-c((numInstances-numTest+1):numInstances)], X5[-c((numInstances-numTest+1):numInstances)])))

# Combine plots into a 2x2 grid
grid.arrange(plot1, plot2, plot3, plot4, ncol=2)

```

-   Plots 1(X-X2) , 2(X2-X3) and 3(X3-X4) have a strong correlation.

-   X4 and X5 are not dependent on each other as evident from graph

    Next, we create 4 additional versions of the training and test sets. The first version, X_train2 and X_test2 have 2 correlated predictor variables, X and X2. The second version, X_train3 and X_test3 have 3 correlated predictor variables, X, X2, and X3. The third version have 4 correlated variables, X, X2, X3, and X4 whereas the last version have 5 correlated variables, X, X2, X3, X4, and X5.

    ```{r}
    # Split data into training and testing sets
    train_indices <- 1:(numInstances - numTest)
    test_indices <- (numInstances - numTest + 1):numInstances

    # Create combined training and testing sets
    X_train2 <- cbind(X[train_indices], X2[train_indices])
    X_test2 <- cbind(X[test_indices], X2[test_indices])

    X_train3 <- cbind(X[train_indices], X2[train_indices], X3[train_indices])
    X_test3 <- cbind(X[test_indices], X2[test_indices], X3[test_indices])

    X_train4 <- cbind(X[train_indices], X2[train_indices], X3[train_indices], X4[train_indices])
    X_test4 <- cbind(X[test_indices], X2[test_indices], X3[test_indices], X4[test_indices])

    X_train5 <- cbind(X[train_indices], X2[train_indices], X3[train_indices], X4[train_indices], X5[train_indices])
    X_test5 <- cbind(X[test_indices], X2[test_indices], X3[test_indices], X4[test_indices], X5[test_indices])
    ```

Below, we train 4 new regression models based on the 4 versions of training and test data created in the previous step.

```{r}
# Convert matrices to tibbles for training
train_data2 <- tibble(X1 = X_train2[,1], X2 = X_train2[,2], y = y_train)
train_data3 <- tibble(X1 = X_train3[,1], X2 = X_train3[,2], X3 = X_train3[,3], y = y_train)
train_data4 <- tibble(X1 = X_train4[,1], X2 = X_train4[,2], X3 = X_train4[,3], X4 = X_train4[,4], y = y_train)
train_data5 <- tibble(X1 = X_train5[,1], X2 = X_train5[,2], X3 = X_train5[,3], X4 = X_train5[,4], X5 = X_train5[,5], y = y_train)

# Train models
regr2_spec <- linear_reg() %>% set_engine("lm")
regr2_fit <- regr2_spec %>% fit(y ~ X1 + X2, data = train_data2)

regr3_spec <- linear_reg() %>% set_engine("lm")
regr3_fit <- regr3_spec %>% fit(y ~ X1 + X2 + X3, data = train_data3)

regr4_spec <- linear_reg() %>% set_engine("lm")
regr4_fit <- regr4_spec %>% fit(y ~ X1 + X2 + X3 + X4, data = train_data4)

regr5_spec <- linear_reg() %>% set_engine("lm")
regr5_fit <- regr5_spec %>% fit(y ~ X1 + X2 + X3 + X4 + X5, data = train_data5)
```

All 4 versions of the regression models are then applied to the training and test sets.

```{r}
# Convert matrices to data.frames for predictions
new_train_data2 <- setNames(as.data.frame(X_train2), c("X1", "X2"))
new_test_data2 <- setNames(as.data.frame(X_test2), c("X1", "X2"))

new_train_data3 <- setNames(as.data.frame(X_train3), c("X1", "X2", "X3"))
new_test_data3 <- setNames(as.data.frame(X_test3), c("X1", "X2", "X3"))

new_train_data4 <- setNames(as.data.frame(X_train4), c("X1", "X2", "X3", "X4"))
new_test_data4 <- setNames(as.data.frame(X_test4), c("X1", "X2", "X3", "X4"))

new_train_data5 <- setNames(as.data.frame(X_train5), c("X1", "X2", "X3", "X4", "X5"))
new_test_data5 <- setNames(as.data.frame(X_test5), c("X1", "X2", "X3", "X4", "X5"))

# Predictions
y_pred_train2 <- predict(regr2_fit, new_data = new_train_data2)
y_pred_test2 <- predict(regr2_fit, new_data = new_test_data2)

y_pred_train3 <- predict(regr3_fit, new_data = new_train_data3)
y_pred_test3 <- predict(regr3_fit, new_data = new_test_data3)

y_pred_train4 <- predict(regr4_fit, new_data = new_train_data4)
y_pred_test4 <- predict(regr4_fit, new_data = new_test_data4)

y_pred_train5 <- predict(regr5_fit, new_data = new_train_data5)
y_pred_test5 <- predict(regr5_fit, new_data = new_test_data5)
```

```{r}
# Extract coefficients and intercepts
get_coef <- function(model) {
  coef <- coefficients(model$fit)
  coef
}

# Calculate RMSE
calculate_rmse <- function(actual, predicted) {
  rmse <- sqrt(mean((actual - predicted)^2))
  rmse
}

results <- tibble(
  Model = c(sprintf("%.2f X + %.2f", get_coef(regr2_fit)['X1'], get_coef(regr2_fit)['(Intercept)']),
            sprintf("%.2f X + %.2f X2 + %.2f", get_coef(regr3_fit)['X1'], get_coef(regr3_fit)['X2'], get_coef(regr3_fit)['(Intercept)']),
            sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f", get_coef(regr4_fit)['X1'], get_coef(regr4_fit)['X2'], get_coef(regr4_fit)['X3'], get_coef(regr4_fit)['(Intercept)']),
            sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f X4 + %.2f", get_coef(regr5_fit)['X1'], get_coef(regr5_fit)['X2'], get_coef(regr5_fit)['X3'], get_coef(regr5_fit)['X4'], get_coef(regr5_fit)['(Intercept)'])),
  
  Train_error = c(calculate_rmse(y_train, y_pred_train2$.pred),
                  calculate_rmse(y_train, y_pred_train3$.pred),
                  calculate_rmse(y_train, y_pred_train4$.pred),
                  calculate_rmse(y_train, y_pred_train5$.pred)),
  
  Test_error = c(calculate_rmse(y_test, y_pred_test2$.pred),
                 calculate_rmse(y_test, y_pred_test3$.pred),
                 calculate_rmse(y_test, y_pred_test4$.pred),
                 calculate_rmse(y_test, y_pred_test5$.pred)),
  
  Sum_of_Absolute_Weights = c(sum(abs(get_coef(regr2_fit))),
                              sum(abs(get_coef(regr3_fit))),
                              sum(abs(get_coef(regr4_fit))),
                              sum(abs(get_coef(regr5_fit))))
)

# Plotting
ggplot(results, aes(x = Sum_of_Absolute_Weights)) +
  geom_line(aes(y = Train_error, color = "Train error"), linetype = "solid") +
  geom_line(aes(y = Test_error, color = "Test error"), linetype = "dashed") +
  labs(x = "Sum of Absolute Weights", y = "Error rate") +
  theme_minimal()
```

-   From the above graph, it is evident that the Error in Testing is very high when compared to Training. This means that the model is overfitting to the training set.

```{r}
results
```

## Ridge Regression

Ridge regression is a statistical method for linear regression that is used to solve problems of multicollinearity. Multicollinearity occurs when two or more predictor variables in a regression model are highly correlated with each other. This can make it difficult to estimate the true coefficients of the predictor variables, and can lead to inaccurate predictions.

```{r}
# Convert to data frame
train_data <- tibble(y = y_train, X_train5)
test_data <- tibble(y = y_test, X_test5)

# Set up a Ridge regression model specification
ridge_spec <- linear_reg(penalty = 0.4, mixture = 1) %>% 
  set_engine("glmnet")

# Fit the model
ridge_fit <- ridge_spec %>% 
  fit(y ~ ., data = train_data)

# Make predictions
y_pred_train_ridge <- predict(ridge_fit, new_data = train_data)$.pred
y_pred_test_ridge <- predict(ridge_fit, new_data = test_data)$.pred


# Make predictions
y_pred_train_ridge <- predict(ridge_fit, new_data = train_data)$.pred
y_pred_test_ridge <- predict(ridge_fit, new_data = train_data)$.pred

# Calculate RMSE
calculate_rmse <- function(actual, predicted) {
  rmse <- sqrt(mean((actual - predicted)^2))
  rmse
}

# Extract coefficients
ridge_coef <- coefficients(ridge_fit$fit)

model6 <- sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f X4 + %.2f X5 + %.2f", 
                 ridge_coef[2], ridge_coef[3], ridge_coef[4], 
                 ridge_coef[5], ridge_coef[6], ridge_coef[1])

values6 <- tibble(
  Model = model6,
  Train_error = calculate_rmse(y_train, y_pred_train_ridge),
  Test_error = calculate_rmse(y_test, y_pred_test_ridge),
  Sum_of_Absolute_Weights = sum(abs(ridge_coef))
)

# Combining the results
final_results <- bind_rows(results, values6)

final_results
```

-   For higher order models, ridge regression has changed the value of the coefficients to 0. This will help in addressing multicollinearity issues, where predictor variables are highly correlated.

-   By setting some coefficients to 0, ridge regression effectively selects a subset of the most important features, promoting model simplicity and preventing overfitting.

-   By setting an appropriate value for the hyperparameter, we can control the sum of absolute weights, thus producing a test error that is quite comparable to that of MLR without the correlated attributes.

-   Ridge Regression has done a good job of reducing the test error and generalizing the model for higher model order.

## **Lasso Regression**

Lasso regression, also known as L1 regularization, is a type of linear regression that uses shrinkage to improve prediction accuracy and interpretability. It achieves this by adding a penalty term to the traditional least squares model, which encourages sparse solutions where some coefficients are forced to be exactly zero. This means that Lasso regression can effectively select relevant features and remove irrelevant ones, leading to a more interpretable model.

```{r}
# Define the lasso specification
lasso_spec <- linear_reg(penalty = 0.02, mixture = 1) %>% 
  set_engine("glmnet")

# Ensure the data is combined correctly
train_data <- tibble(y = y_train, X1 = X_train5[,1], X2 = X_train5[,2], 
                     X3 = X_train5[,3], X4 = X_train5[,4], X5 = X_train5[,5])

# Fit the model
lasso_fit <- lasso_spec %>%
  fit(y ~ ., data = train_data)

# Extract coefficients
lasso_coefs <- lasso_fit$fit$beta[,1]

# Predictions
y_pred_train_lasso <- predict(lasso_fit, new_data = train_data)$.pred
y_pred_test_lasso <- predict(lasso_fit, new_data = tibble(X1 = X_test5[,1], X2 = X_test5[,2], 
                                                          X3 = X_test5[,3], X4 = X_test5[,4], X5 = X_test5[,5]))$.pred

# Create the model string
model7 <- sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f X4 + %.2f X5 + %.2f", 
                  lasso_coefs[2], lasso_coefs[3], lasso_coefs[4], 
                  lasso_coefs[5], lasso_coefs[6], lasso_fit$fit$a0[1])

values7 <- c(model7, 
             sqrt(mean((y_train - y_pred_train_lasso)^2)),
             sqrt(mean((y_test - y_pred_test_lasso)^2)),
             sum(abs(lasso_coefs[-1])) + abs(lasso_fit$fit$a0[1]))

# Make the results tibble
lasso_results <- tibble(Model = "Lasso",
                        `Train error` = values7[2], 
                        `Test error` = values7[3], 
                        `Sum of Absolute Weights` = values7[4])

lasso_results
```

-   There is marginal improvement in the errors. Lasso regression has set the coefficients to 0, thus promoting model simplicity.

## **Hyperparameter Selection via Cross-Validation**

While both ridge and lasso regression methods can potentially alleviate the model overfitting problem, one of the challenges is how to select the appropriate hyperparameter value, α. In the examples shown below, we demonstrate examples of using a 5-fold cross-validation method to select the best hyperparameter of the model. More details about the model selection problem and cross-validation method are described in Chapter 3 of the book.

In the first sample code below, we vary the hyperparameter α for ridge regression to a range between 0.2 and 1.0. Using the `RidgeCV()` function, we can train a model with 5-fold cross-validation and select the best hyperparameter value.

```{r}
# Combine training data
y_train <- as.vector(y_train)

train_data <- tibble(y = y_train, X1 = X_train5[,1], X2 = X_train5[,2], 
                     X3 = X_train5[,3], X4 = X_train5[,4], X5 = X_train5[,5])

# Define recipe
recipe_obj <- recipe(y ~ ., data = train_data) %>%
  step_normalize(all_predictors()) |>
  prep()

# Define the ridge specification
ridge_spec <- linear_reg(penalty = tune(), mixture = 0) %>% 
  set_engine("glmnet")

# Ridge workflow
ridge_wf <- workflow() |>
  add_model(ridge_spec) |>
  add_recipe(recipe_obj)

# Grid of alphas
alphas <- tibble(penalty = c(0.2, 0.4, 0.6, 0.8, 1.0))

# Tune
tune_results <- 
  ridge_wf |>
  tune_grid(
  resamples = bootstraps(train_data, times = 5),
  grid = alphas
)


# Extract best parameters
best_params <- tune_results %>% select_best("rmse")

# Refit the model
ridge_fit <- ridge_spec %>%
  finalize_model(best_params) %>%
  fit(y ~ ., data = train_data)

# Extract coefficients
ridge_coefs <- ridge_fit$fit$beta[,1]

# Predictions
y_pred_train_ridge <- predict(ridge_fit, new_data = train_data)$.pred
y_pred_test_ridge <- predict(ridge_fit, new_data = tibble(X1 = X_test5[,1], X2 = X_test5[,2], 
                                                          X3 = X_test5[,3], X4 = X_test5[,4], X5 = X_test5[,5]))$.pred

# Create the model string
model6 <- sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f X4 + %.2f X5 + %.2f", 
                  ridge_coefs[2], ridge_coefs[3], ridge_coefs[4], 
                  ridge_coefs[5], ridge_coefs[6], ridge_fit$fit$a0[1])

values6 <- c(model6, 
             sqrt(mean((y_train - y_pred_train_ridge)^2)),
             sqrt(mean((y_test - y_pred_test_ridge)^2)),
             sum(abs(ridge_coefs[-1])) + abs(ridge_fit$fit$a0[1]))

# Make the results tibble
ridge_results <- tibble(Model = "RidgeCV",
                        `Train error` = values6[2], 
                        `Test error` = values6[3], 
                        `Sum of Absolute Weights` = values6[4])

cat("Selected alpha =", best_params$penalty, "\n")




```

-   Hyperparameter is selected as 0.2

```{r}
all_results <- bind_rows(results, ridge_results)
all_results
```

-   There is minimal to no improvement when using hyperparameter selection.

Applying Cross-Validation

```{r}
set.seed(1234)

# Ensure y_train is a vector
y_train <- as.vector(y_train)

# Combine training data
train_data <- tibble(y = y_train, X1 = X_train5[,1], X2 = X_train5[,2], 
                     X3 = X_train5[,3], X4 = X_train5[,4], X5 = X_train5[,5])

# Define recipe
recipe_obj_lasso <- recipe(y ~ ., data = train_data) %>%
  step_normalize(all_predictors()) |>
  prep()

# Define the lasso specification
lasso_spec <- linear_reg(penalty = tune(), mixture = 1) %>% 
  set_engine("glmnet")

# Lasso workflow
lasso_wf <- workflow() |>
  add_recipe(recipe_obj_lasso)

# Lasso fit
lasso_fit <- lasso_wf |>
  add_model(lasso_spec) |>
  fit(data = train_data)

# Grid of alphas for Lasso
lambda_grid <- grid_regular(penalty(), levels = 50)

# Tune
tune_results_lasso <- 
  tune_grid(lasso_wf |> add_model(lasso_spec),
  resamples = bootstraps(train_data, times = 5),
  grid = lambda_grid
)

# Extract best parameters for Lasso
best_params_lasso <- tune_results_lasso %>% select_best("rmse")

# Refit the model using Lasso
lasso_fit <- lasso_spec %>%
  finalize_model(best_params_lasso) %>%
  fit(y ~ ., data = train_data)

# Extract coefficients
lasso_coefs <- lasso_fit$fit$beta[,1]

# Predictions using Lasso
y_pred_train_lasso <- predict(lasso_fit, new_data = train_data)$.pred
y_pred_test_lasso <- predict(lasso_fit, new_data = tibble(X1 = X_test5[,1], X2 = X_test5[,2], 
                                                          X3 = X_test5[,3], X4 = X_test5[,4], X5 = X_test5[,5]))$.pred

# Create the model string for Lasso
model7 <- sprintf("%.2f X + %.2f X2 + %.2f X3 + %.2f X4 + %.2f X5 + %.2f", 
                  lasso_coefs[2], lasso_coefs[3], lasso_coefs[4], 
                  lasso_coefs[5], lasso_coefs[6], lasso_fit$fit$a0[1])

values7 <- c(model7, 
             sqrt(mean((y_train - y_pred_train_lasso)^2)),
             sqrt(mean((y_test - y_pred_test_lasso)^2)),
             sum(abs(lasso_coefs[-1])) + abs(lasso_fit$fit$a0[1]))

# Make the results tibble for Lasso
lasso_results <- tibble(Model = "LassoCV",
                        `Train error` = values7[2], 
                        `Test error` = values7[3], 
                        `Sum of Absolute Weights` = values7[4])

cat("Selected alpha for Lasso =", best_params_lasso$penalty, "\n")
```

```{r}
lasso_results
```

-   Lasso regression has worked better on hyperparameter selection than the previous. The test error is significantly reduced.

## Answer of the proposed question: How do daily opening prices, trading volumes, and historical trends influence the adjusted closing prices of stocks?

The relationship between opening prices and the adjusted closing price of the stock is notably strong, as indicated by the results of a linear regression analysis. However, when employing multiple regression, the model's performance deteriorated, primarily due to the presence of high collinearity among the features
